PANCHANGE_analysis

### 2021-03-09 PANCHANGE_analysis.Rmd
reordered explanatory variables for forest plots to match legend

```{r merge datasets for different combinations}
# Disorder groups
plot.dat.disorder.prepan <- rbind(gad.prepan.lm.for.plot,
                                  phq.prepan.lm.for.plot,
                                  pcl.prepan.lm.for.plot)

plot.dat.disorder.retro <- rbind(gad.retro.lm.for.plot,
                                  phq.retro.lm.for.plot,
                                  pcl.retro.lm.for.plot)

@@

plot.dat.disorder <- plot.dat.disorder %>%
  mutate(RowLabels = recode(RowLabels,
                            `PCL.prepandemic` = "PCL total prepandemic",
                            `PHQ.prepandemic` = "PHQ total prepandemic",
                            `GAD.prepandemic` = "GAD total prepandemic"
                            ))

@@

>>>>

```{r merge datasets for different combinations}
# Disorder groups
plot.dat.disorder.prepan <- rbind(gad.prepan.lm.for.plot,
                                  pcl.prepan.lm.for.plot,
                                  phq.prepan.lm.for.plot)

plot.dat.disorder.retro <- rbind(gad.retro.lm.for.plot,
                                  pcl.retro.lm.for.plot,
                                 phq.retro.lm.for.plot)

@@

@@

plot.dat.disorder.prepan <- plot.dat.disorder.prepan %>%
  mutate(RowLabels = recode(RowLabels,
                            `PCL.prepandemic` = "PCL total prepandemic",
                            `PHQ.prepandemic` = "PHQ total prepandemic",
                            `GAD.prepandemic` = "GAD total prepandemic"))
